Epilepsy example

### 2022-11-15 src/docs_15-11-22-seminar/15-11-22-seminar.Rmd
Slides up!

# Comparison approach

* You could look at the summaries like the mean and standard deviation of each of the posterior marginals but it's better to compare the whole posterior distributions
* One way to do this is via Kolmogorov-Smirnov statistics, which give the maximum difference between two empirical CDFs

@@

* Notebook for this example at `athowes.github.io/elgm-inf/prev-anc-art`
* Simulate data from model with all three components and particular (known) parameter values

@@

@@

* Joint work with Alex Stringer (Waterloo) and my supervisors Seth Flaxman (Oxford) and Jeff Eaton (Imperial)
* The code for this project is at `github.com/athowes/elgm-inf`
* You can find me online at `athowes.github.io`

>>>>

```{r echo=FALSE}
df <- readRDS("depends/comparison-results.rds") %>%
  select("tmbstan", "R-INLA_G", "R-INLA_SL", "R-INLA_L", "TMB", "aghq", "adam")

beta_i <- function(i) { c(paste0("$\\mathbb{E}[\\beta_", i, "]$"), paste0("$\\text{sd}[\\beta_", i, "]$")) }
rownames(df) <- c(sapply(0:5, beta_i))

names(df) <- c("\\texttt{tmbstan}", "\\texttt{R-INLA}-G", "\\texttt{R-INLA}-SL", "\\texttt{R-INLA}-L", "\\texttt{TMB}", "\\texttt{aghq}", "\\texttt{adam}")

df %>%
  kableExtra::kable(format = "latex", align = "l", booktabs = TRUE, longtable = TRUE, digits = 2, escape = FALSE)
```

```{r message=FALSE, echo=FALSE, out.height="200px", fig.cap=paste("The intercept parameter has the greatest difference between the Gaussian and Laplace approaches. The results in pink are from HMC NUTS.")}
knitr::include_graphics("depends/intercept-comparison.pdf")
```

# Comparison approaches

* You could look at the summaries like the mean and standard deviation of each of the posterior marginals as we have above
* It worked for $\beta_0$, but usually this isn't very informative, and it's better to compare the whole posterior distributions
* One way to do this is via Kolmogorov-Smirnov statistics, which give the maximum difference between two empirical CDFs
* Also considering other approaches!
  * PSIS: is your approximate distribution a good importance sampling proposal for your target? If not, maybe there is an issue!
  * SBC: generating $(\theta, y)$ first $\theta$ then $y \ | \ \theta$ should be the same as first $y$ then then $\theta \ | \ y$
  * MMD: compute a distance using kernels (e.g. Gaussian)

@@

* Simulate data from model with all three components and particular (known) parameter values

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
Notebook for this example at \texttt{athowes.github.io/elgm-inf/prev-anc-art}
\end{tcolorbox}
\end{center}

@@

```{r message=FALSE, echo=FALSE, out.height="200px", fig.cap=paste("Example KS results from five simulated datasets.")}
knitr::include_graphics("depends/ks-example.pdf")
```

@@

* Joint work with Alex Stringer (Waterloo) and my PhD supervisors Seth Flaxman (Oxford) and Jeff Eaton (Imperial)
* The code for this project is at `github.com/athowes/elgm-inf`
* You can find me online at `athowes.github.io`

### 2022-11-15 src/epil/epil.Rmd
Slides up!

beta0_inla_marginals <- bind_rows(
  data.frame(fit2$marginals.fixed$`(Intercept)`) %>%
    mutate(method = "G"),
  data.frame(fit3$marginals.fixed$`(Intercept)`) %>%
    mutate(method = "SL"),
  data.frame(fit4$marginals.fixed$`(Intercept)`) %>%
    mutate(method = "L")
)

plot_pdf +
  geom_line(data = beta0_inla_marginals, aes(x = x, y = y, col = method)) +
  scale_color_manual(values = cbpalette)
```

>>>>

beta0_inla_marginals <- bind_rows(
  data.frame(fit2$marginals.fixed$`(Intercept)`) %>%
    mutate(method = "Gaussian"),
  data.frame(fit4$marginals.fixed$`(Intercept)`) %>%
    mutate(method = "Laplace")
)

plot_pdf <- plot_pdf +
  geom_line(data = beta0_inla_marginals, aes(x = x, y = y, col = method)) +
  scale_color_manual(values = cbpalette) +
  labs(col = "Method")

plot_pdf

ggsave("intercept-comparison.pdf", plot = plot_pdf, h = 4, w = 6.25)
```
